Geometric Control for Autonomous Landing on Asteroids

### 2017-08-08 manuscript.tex
Add a summary of ORB-SLAM

We seek to utilize well-proven methods in the computer vision and robotics community to first localize the position of the spacecraft from visual imagery.
A secondary step, which is left to a subsequent publication, is then to use this imagery to autonomously update the position of the spacecraft while simultaneously mapping the surface. 
We utilize the state of the art ORB-SLAM implementation to estimate the state of the spacecraft using monocular images~\cite{mur-artal2015}.

% TODO: Cite ORB-SLAM2 paper
% TODO: Give a brief overview of the method

One first step is to enable autonomous navigation and control

Use image sensors for localization and can extend to mapping

We demonstrate the ability to estimate location using monocular images
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth,keepaspectratio]{figures/itokawa_feature_matching.png}
    \caption{Demonstration of feature detection and matching between simulated images of asteroid 25413 Itokawa}
    \label{fig:itokawa_feature_matching}
\end{figure}
\section{Numerical Simulation}\label{sec:simulation}

>>>>

We seek to utilize well-proven methods in the computer vision and robotics community to first localize the position of the spacecraft from visual imagery.
A secondary step, which is left to a subsequent publication, is then to use this imagery to autonomously update the position of the spacecraft while simultaneously mapping the surface. 
We utilize the state of the art ORB-SLAM implementation to estimate the state of the spacecraft using monocular images~\cite{mur-artal2015}.
This method provides a feature based monocular SLAM system that can operate in real-time for a wide variety of environments. 
ORB-SLAM builds on proven methods in the robotics community to create a custom SLAM system that provides for autonomous tracking and mapping in an unknown environment. 
The first step in ORB-SLAM is to determine accurate features within an image that are most easily recognized in subsequent images. 
This ``feature-extraction'' stage uses the FAST feature detector to determine suitable features, and then the ORB feature descriptor to a store a compact, scale-invariant description of the feature properties.
Next, these features are matched to subsequent images in a ``feature-matching'' stage to determine correspondance between subsequent images. 
For example,~\cref{fig:itokawa_feature_matching} shows a demonstration of features computed in two view of asteroid Itokawa. 
In addition, the correspondance is accurately computed between matching features as shown by the horizontal lines across both images.
From these correspondances, the pose of the camera system is estimated and predicted forward in time using a constant velocity model.
In a simultaenous thread, the ORB-SLAM system builds a local map and stores feature data in order to perform loop closure in the event of returning to a previously imaged location.
We utilize ORB-SLAM to provide an estimate of the position of the rigid spacecraft and will use this estimate to compute the control input.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth,keepaspectratio]{figures/itokawa_feature_matching.png}
    \caption{Demonstration of feature detection and matching between simulated images of asteroid 25413 Itokawa}
    \label{fig:itokawa_feature_matching}
\end{figure}
\section{Numerical Simulation}\label{sec:simulation}
